A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-02 article/article.tex

>>>>

CARLA (Car Learning to Act) is an open-source simulator specifically designed for autonomous driving research and development. It provides a highly realistic urban driving environment with diverse road layouts, weather conditions, and traffic scenarios. The simulator features a comprehensive sensor suite simulation, flexible API for scenario creation, and supports both learning-based and traditional autonomous driving approaches. CARLA enables researchers to test and validate autonomous vehicle systems in a safe, controllable environment before real-world deployment.

The simulator has gained widespread adoption across both academic and industrial settings. In research, CARLA serves as a standard platform for developing and 
benchmarking autonomous driving algorithms, including reinforcement learning approaches for vehicle control and sensor fusion techniques \cite{codevilla2019exploringlimitationsbehaviorcloning}. Industry applications include 
virtual testing of production autonomous vehicle systems, scenario-based validation pipelines, and integration with hardware-in-the-loop testing frameworks \cite{jaeger2023hiddenbiasesendtoenddriving}. CARLA is also extensively used in autonomous driving competitions and challenges, providing a common evaluation environment for comparing different approaches across research groups worldwide.
